---
title: "Sevilla FC Strategy Dashboard"
output:
  html_document:
    self_contained: false
    theme: null
    toc: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  error = FALSE,
  results = "asis"
)

library(plotly)
library(htmlwidgets)
library(htmltools)



possible_code_files <- c("R_code.R")
r_code_file <- possible_code_files[file.exists(possible_code_files)][1]
if (is.na(r_code_file)) {
  stop("No R code file was found. Put this Rmd file in the same folder as R_code.R or R_code_updated_for_submission.R before knitting.")
}

# -----------------------------
# Robust data folder detection
# -----------------------------

possible_data_dirs <- c(
  "Data",
  "data",
  ".",
  "C:/Users/adnan/OneDrive/Desktop/sevilla_R/Data",
  "C:/Users/adnan/OneDrive/Desktop/sevilla_R"
)

data_dir <- possible_data_dirs[
  file.exists(file.path(possible_data_dirs, "Match.csv"))
][1]

if (is.na(data_dir)) {
  stop(
    "Could not find Match.csv. Please put the CSV files in a folder called 'Data' ",
    "next to this Rmd file, or update possible_data_dirs with the correct path."
  )
}

cat("Using data folder:", data_dir, "\n")
# Use the folder that actually contains Match.csv.
auto_data_dir <- normalizePath(data_dir, winslash = "/", mustWork = TRUE)

code_lines <- readLines(r_code_file, warn = FALSE)
if (!is.na(auto_data_dir)) {
  idx <- grep('^\\s*data_dir\\s*<-\\s*"', code_lines)
  if (length(idx) > 0) {
    code_lines[idx[1]] <- paste0('data_dir <- "', auto_data_dir, '"')
  }
}

invisible(capture.output(
  eval(parse(text = paste(code_lines, collapse = "\n")), envir = knitr::knit_global())
))

required_objects <- c(
  "interactive_spanish_teams",
  "interactive_possession_bands",
  "interactive_young_players"
)
missing_objects <- required_objects[!vapply(required_objects, exists, logical(1), envir = knitr::knit_global())]
if (length(missing_objects) > 0) {
  stop("The following Plotly objects were not created by R_code.R: ", paste(missing_objects, collapse = ", "))
}

widget_dir <- "vds_plotly_widgets_nocrop"
if (!dir.exists(widget_dir)) dir.create(widget_dir, recursive = TRUE)

# Prepare plot for full-screen embedding.
# We keep the original visualisation but make Plotly responsive and give margins
# that leave enough space for axis titles and annotations.
prepare_plot <- function(p, margin = list(l = 95, r = 95, t = 95, b = 95)) {
  p %>%
    layout(
      autosize = TRUE,
      margin = margin,
      paper_bgcolor = "white",
      plot_bgcolor = "white"
    ) %>%
    config(
      responsive = TRUE,
      displaylogo = FALSE,
      modeBarButtonsToRemove = c("lasso2d", "select2d")
    )
}

# This patch is the important part: it forces the saved widget to exactly match
# the iframe size. Plotly::Plots.resize alone sometimes keeps the old RStudio size,
# causing the lower half to be clipped in knitted slides.
patch_widget_html <- function(file) {
  x <- readLines(file, warn = FALSE)
  css_js <- paste0(
    "\n<style>",
    "html, body {width:100vw; height:100vh; margin:0; padding:0; overflow:hidden; background:white;}",
    ".html-widget, .plotly, .plot-container, .svg-container {width:100vw !important; height:100vh !important;}",
    "</style>\n",
    "<script>",
    "function fitPlotlyToWindow(){",
    "  var w = Math.max(document.documentElement.clientWidth, window.innerWidth || 0);",
    "  var h = Math.max(document.documentElement.clientHeight, window.innerHeight || 0);",
    "  var widgets = document.querySelectorAll('.html-widget, .plotly, .plot-container, .svg-container');",
    "  widgets.forEach(function(el){ el.style.width = w + 'px'; el.style.height = h + 'px'; });",
    "  var gd = document.querySelector('.plotly');",
    "  if(gd && window.Plotly){",
    "    try { window.Plotly.relayout(gd, {width: w, height: h}); } catch(e) {}",
    "    try { window.Plotly.Plots.resize(gd); } catch(e) {}",
    "  }",
    "}",
    "window.addEventListener('load', function(){ fitPlotlyToWindow(); setTimeout(fitPlotlyToWindow, 200); setTimeout(fitPlotlyToWindow, 800); setTimeout(fitPlotlyToWindow, 1500); });",
    "window.addEventListener('resize', fitPlotlyToWindow);",
    "</script>\n"
  )
  x <- sub("</head>", paste0(css_js, "</head>"), x, fixed = TRUE)
  writeLines(x, file)
}

save_full_widget <- function(p, filename, libdir, margin = list(l = 95, r = 95, t = 95, b = 95)) {
  p <- prepare_plot(p, margin = margin)
  p$sizingPolicy <- htmlwidgets::sizingPolicy(
    browser.fill = TRUE,
    viewer.fill = TRUE,
    padding = 0,
    defaultWidth = "100%",
    defaultHeight = "100%"
  )
  file_path <- file.path(widget_dir, filename)
  saveWidget(p, file = file_path, selfcontained = FALSE, libdir = libdir)
  patch_widget_html(file_path)
}

save_full_widget(interactive_spanish_teams, "visual1_team_position.html", "visual1_files")

# Rebuild the possession figure specifically for the HTML slides.
# Reason: after knitting/iframe embedding, Plotly sometimes hides the bar trace
# labels. This version uses Plotly annotations placed at the centre of each
# stacked segment, so the percentages remain visible after knitting.
# It also removes the external legend and replaces it with a compact inline
# legend above the plot, avoiding the overlap/truncation problem.
if (!exists("counts", envir = knitr::knit_global()) || !exists("summary_possession", envir = knitr::knit_global())) {
  stop("counts and summary_possession were not created by R_code.R. Please run the original R code successfully first.")
}

result_order_slides <- c("Loss", "Draw", "Win")
result_colors_slides <- c(
  "Loss" = "#D71920",
  "Draw" = "#F28E2B",
  "Win"  = "#2CA02C"
)

counts_slides <- counts %>%
  dplyr::mutate(
    result = factor(as.character(result), levels = result_order_slides),
    possession_band = factor(as.character(possession_band), levels = bands, ordered = TRUE),
    pct_label = dplyr::if_else(
      is.na(percentage) | percentage <= 0,
      "",
      paste0(round(percentage), "%")
    ),
    tooltip_slide = paste0(
      "Possession band: ", possession_band,
      "<br>Result: ", result,
      "<br>Matches: ", count,
      "<br>Total in band: ", total,
      "<br>Share: ", round(percentage, 1), "%"
    )
  ) %>%
  dplyr::arrange(possession_band, result)

summary_slides <- summary_possession %>%
  dplyr::mutate(
    possession_band = factor(as.character(possession_band), levels = bands, ordered = TRUE),
    top_label = paste0("n = ", n_matches, " | pts = ", round(avg_points, 2))
  ) %>%
  dplyr::arrange(possession_band)

best_row_slides <- summary_slides %>%
  dplyr::filter(avg_points == max(avg_points, na.rm = TRUE)) %>%
  dplyr::slice(1)

# Calculate annotation y-positions at the centre of each stacked segment.
# This is more reliable than textposition = "inside" after knitting.
annotation_data <- counts_slides %>%
  dplyr::group_by(possession_band) %>%
  dplyr::arrange(result, .by_group = TRUE) %>%
  dplyr::mutate(
    y_bottom = dplyr::lag(cumsum(percentage), default = 0),
    y_mid = y_bottom + percentage / 2,
    text_col = dplyr::case_when(
      result == "Draw" ~ "#222222",
      TRUE ~ "white"
    )
  ) %>%
  dplyr::ungroup() %>%
  dplyr::filter(percentage > 0)

pct_annotations <- lapply(seq_len(nrow(annotation_data)), function(i) {
  list(
    x = as.character(annotation_data$possession_band[i]),
    y = annotation_data$y_mid[i],
    text = annotation_data$pct_label[i],
    showarrow = FALSE,
    xanchor = "center",
    yanchor = "middle",
    font = list(
      size = 15,
      color = annotation_data$text_col[i],
      family = "Arial"
    )
  )
})

top_annotations <- lapply(seq_len(nrow(summary_slides)), function(i) {
  list(
    x = as.character(summary_slides$possession_band[i]),
    y = 103,
    text = summary_slides$top_label[i],
    showarrow = FALSE,
    xanchor = "center",
    yanchor = "bottom",
    font = list(size = 12, color = "#222222", family = "Arial")
  )
})

# Legend is kept as coloured square symbols in the Plotly subtitle.
# This avoids using separate legend annotations, which overlapped with the title after knitting.
best_annotation <- list(
  list(
    x = as.character(best_row_slides$possession_band),
    y = 100,
    text = paste0(
      "Best band: ", as.character(best_row_slides$possession_band),
      "<br>", round(best_row_slides$avg_points, 2), " pts/match"
    ),
    showarrow = TRUE,
    ax = 70,
    ay = -62,
    arrowhead = 2,
    arrowwidth = 1.2,
    arrowcolor = "#333333",
    font = list(size = 11, color = "#111111", family = "Arial")
  )
)

possession_plot_for_slides <- plot_ly()

for (res in result_order_slides) {
  plot_data <- counts_slides %>% dplyr::filter(result == res)
  possession_plot_for_slides <- possession_plot_for_slides %>%
    add_trace(
      data = plot_data,
      x = ~possession_band,
      y = ~percentage,
      type = "bar",
      name = res,
      showlegend = FALSE,
      marker = list(
        color = result_colors_slides[[res]],
        line = list(color = "white", width = 1)
      ),
      hoverinfo = "text",
      hovertext = ~tooltip_slide,
      cliponaxis = FALSE
    )
}

possession_plot_for_slides <- possession_plot_for_slides %>%
  layout(
    barmode = "stack",
    showlegend = FALSE,
    title = list(
      text = paste0(
        "Sevilla FC results by possession band",
        "<br><sup>",
        "Win = 3 points | Draw = 1 point | Loss = 0 points",
        "<br>",
        "<span style='color:#D71920;font-size:16px;'>&#9632;</span> Loss &nbsp;&nbsp;",
        "<span style='color:#F28E2B;font-size:16px;'>&#9632;</span> Draw &nbsp;&nbsp;",
        "<span style='color:#2CA02C;font-size:16px;'>&#9632;</span> Win",
        "</sup>"
      ),
      x = 0.5,
      xanchor = "center"
    ),
    font = common_layout$font,
    paper_bgcolor = common_layout$paper_bgcolor,
    plot_bgcolor = common_layout$plot_bgcolor,
    hoverlabel = common_layout$hoverlabel,
    xaxis = c(
      axis_style("Sevilla possession band"),
      list(categoryorder = "array", categoryarray = bands)
    ),
    yaxis = c(
      axis_style("Share of matches (%)"),
      list(range = c(0, 116), ticksuffix = "%")
    ),
    annotations = c(
      pct_annotations,
      top_annotations,
      best_annotation
    ),
    margin = list(t = 155, r = 70, b = 90, l = 90)
  ) %>%
  config(responsive = TRUE, displaylogo = FALSE)

save_full_widget(
  possession_plot_for_slides,
  "visual2_possession.html",
  "visual2_files",
  margin = list(l = 90, r = 70, t = 155, b = 90)
)

save_full_widget(interactive_young_players, "visual3_players.html", "visual3_files")

widget_path <- function(filename) file.path(widget_dir, filename)

open_slide <- function(class = "") {
  cat(sprintf('\n<section class="slide %s">\n', class))
}
close_slide <- function() cat('\n</section>\n')

# Full-screen plot slide: no extra HTML title. The Plotly object already has a title.
plot_slide <- function(src) {
  cat('\n<section class="slide plot-slide">\n')
  cat(sprintf('<iframe class="plot-iframe" src="%s" loading="eager"></iframe>\n', src))
  cat('\n</section>\n')
}
```

```{r css-and-js, results='asis'}
cat('
<style>
html, body {
  margin: 0 !important;
  padding: 0 !important;
  width: 100vw;
  height: 100vh;
  overflow: hidden;
  background: white;
  font-family: Arial, Helvetica, sans-serif;
}
.main-container, .container-fluid, .container {
  max-width: none !important;
  width: 100vw !important;
  height: 100vh !important;
  margin: 0 !important;
  padding: 0 !important;
}
#header { display: none; }

.slide {
  display: none;
  box-sizing: border-box;
  width: 100vw;
  height: 100vh;
  padding: 58px 76px 54px 76px;
  background: white;
  color: #111827;
  overflow: hidden;
}
.slide.active { display: block; }
.slide h1 {
  margin: 0 0 18px 0;
  font-size: 44px;
  line-height: 1.12;
  font-weight: 700;
  color: #111827;
}
.slide h2 {
  margin: 20px 0 12px 0;
  font-size: 31px;
  color: #1f2937;
}
.slide p, .slide li {
  font-size: 27px;
  line-height: 1.38;
  color: #374151;
}
.kicker {
  font-size: 23px !important;
  letter-spacing: .02em;
  color: #4f46e5 !important;
  font-weight: 700;
  text-transform: uppercase;
}
.two-col {
  display: grid;
  grid-template-columns: 1fr 1fr;
  gap: 42px;
  align-items: start;
}
.card {
  border: 1px solid #e5e7eb;
  border-radius: 18px;
  padding: 24px 28px;
  background: #f9fafb;
}
.takeaway {
  margin-top: 26px;
  padding: 18px 24px;
  border-left: 9px solid #4f46e5;
  background: #eef2ff;
  border-radius: 12px;
  font-size: 28px;
  line-height: 1.35;
  color: #1f2937;
}
.plot-slide {
  padding: 0 !important;
  margin: 0 !important;
  overflow: hidden !important;
  background: white;
}
.plot-iframe {
  position: absolute;
  left: 0;
  top: 0;
  display: block;
  width: 100vw;
  height: 100vh;
  border: 0;
  margin: 0;
  padding: 0;
  overflow: hidden;
  background: white;
}
.nav {
  position: fixed;
  right: 18px;
  bottom: 14px;
  z-index: 9999;
  display: flex;
  align-items: center;
  gap: 10px;
  font-size: 15px;
  color: #4b5563;
  background: rgba(255,255,255,0.72);
  padding: 5px 7px;
  border-radius: 10px;
}
.nav button {
  border: 1px solid #d1d5db;
  background: white;
  color: #111827;
  border-radius: 8px;
  padding: 5px 10px;
  cursor: pointer;
  box-shadow: 0 1px 3px rgba(0,0,0,0.10);
}

.hero {
  font-size: 34px !important;
  line-height: 1.25 !important;
  max-width: 980px;
  color: #1f2937 !important;
}
.goal-grid {
  display: grid;
  grid-template-columns: repeat(3, 1fr);
  gap: 22px;
  margin-top: 26px;
}
.goal-card {
  border: 1px solid #e5e7eb;
  border-radius: 18px;
  padding: 22px 24px;
  background: #f9fafb;
  min-height: 170px;
}
.goal-card h2 { font-size: 26px; margin-top: 0; }
.goal-card p { font-size: 23px; line-height: 1.32; }
.big-number {
  font-size: 44px;
  font-weight: 800;
  color: #4f46e5;
  margin-bottom: 8px;
}
.checklist li { margin-bottom: 12px; }
.compact li { font-size: 25px; margin-bottom: 10px; }

.progress {
  position: fixed;
  left: 0;
  bottom: 0;
  height: 5px;
  background: #4f46e5;
  width: 0%;
  z-index: 9998;
}
</style>

<script>
document.addEventListener("DOMContentLoaded", function(){
  const slides = Array.from(document.querySelectorAll("section.slide"));
  let idx = 0;
  const progress = document.createElement("div");
  progress.className = "progress";
  document.body.appendChild(progress);
  const nav = document.createElement("div");
  nav.className = "nav";
  nav.innerHTML = `<button id="prevSlide">◀</button><span id="slideCount"></span><button id="nextSlide">▶</button>`;
  document.body.appendChild(nav);

  function resizeIframePlot(iframe) {
    if (!iframe) return;
    iframe.style.width = window.innerWidth + "px";
    iframe.style.height = window.innerHeight + "px";
    try {
      iframe.contentWindow.dispatchEvent(new Event("resize"));
      if (iframe.contentWindow.fitPlotlyToWindow) iframe.contentWindow.fitPlotlyToWindow();
    } catch(e) {}
  }

  function show(i){
    idx = Math.max(0, Math.min(i, slides.length - 1));
    slides.forEach((s, j) => s.classList.toggle("active", j === idx));
    document.getElementById("slideCount").textContent = (idx + 1) + " / " + slides.length;
    progress.style.width = (((idx + 1) / slides.length) * 100) + "%";
    resizeIframePlot(slides[idx].querySelector("iframe"));
    setTimeout(() => resizeIframePlot(slides[idx].querySelector("iframe")), 250);
    setTimeout(() => resizeIframePlot(slides[idx].querySelector("iframe")), 900);
  }

  document.getElementById("prevSlide").onclick = () => show(idx - 1);
  document.getElementById("nextSlide").onclick = () => show(idx + 1);
  document.addEventListener("keydown", function(e){
    if(["ArrowRight", "PageDown", " "].includes(e.key)) { e.preventDefault(); show(idx + 1); }
    if(["ArrowLeft", "PageUp", "Backspace"].includes(e.key)) { e.preventDefault(); show(idx - 1); }
  });
  window.addEventListener("resize", () => show(idx));
  show(0);
});
</script>
')
```


```{r slide-1, results='asis'}
open_slide()
```

<p class="kicker">Group 7 · Football dataset · Sevilla FC</p>

# Sevilla FC strategy dashboard

<p class="hero">Our project uses the European football dataset from 2008 to 2016 to support one practical strategy question for Sevilla FC.</p>

<div class="goal-grid">
<div class="goal-card">
<div class="big-number">1</div>
<h2>Attack & defence</h2>
<p>How does Sevilla compare with Spanish teams?</p>
</div>
<div class="goal-card">
<div class="big-number">2</div>
<h2>Possession</h2>
<p>Which possession bands are linked to better outcomes?</p>
</div>
<div class="goal-card">
<div class="big-number">3</div>
<h2>Recruitment</h2>
<p>Which young players could be promising targets for 2016?</p>
</div>
</div>

```{r slide-1-close, results='asis'}
close_slide()
```

```{r slide-2, results='asis'}
cat('\n<section class="slide plot-slide">\n')
cat(sprintf('<iframe class="plot-iframe" src="%s" loading="eager"></iframe>\n', widget_path("visual1_team_position.html")))
cat('\n</section>\n')
```

```{r slide-3, results='asis'}
cat('\n<section class="slide plot-slide">\n')
cat(sprintf('<iframe class="plot-iframe" src="%s" loading="eager"></iframe>\n', widget_path("visual2_possession.html")))
cat('\n</section>\n')
```

```{r slide-4, results='asis'}
cat('\n<section class="slide plot-slide">\n')
cat(sprintf('<iframe class="plot-iframe" src="%s" loading="eager"></iframe>\n', widget_path("visual3_players.html")))
cat('\n</section>\n')
```

```{r slide-5, results='asis'}
open_slide()
```

# Conclusion

<div class="goal-grid">
<div class="goal-card">
<h2>Team level</h2>
<p>Sevilla is positioned against Spanish teams using attack, defence, and points context.</p>
</div>
<div class="goal-card">
<h2>Match level</h2>
<p>Possession is interpreted through wins, draws, losses, and average points.</p>
</div>
<div class="goal-card">
<h2>Player level</h2>
<p>Recruitment is supported by age, potential, and attacking contribution.</p>
</div>
</div>

<div class="takeaway">Together, the visuals move from <strong>team performance</strong>, to <strong>tactical interpretation</strong>, to <strong>possible player recruitment</strong>.</div>

```{r slide-5-close, results='asis'}
close_slide()
```
